---
title: "persephone"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{persephone}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

This vignette contains general information on the package. It is intended to give the user a general picture of the package features, presenting the code architecture in a clear and concise way.

The package includes a dataset of the corn and soybeans progress in Nebraska for 20 seasons, from 2002 to 2021. The user can easily draw data from the Demeter database to create a different dataset. More details can be found in the [cronus Github repository](https://github.com/agesofman/cronus "cronus Github repository").

```{r setup}
library(cronus)
library(persephone)

# Create a Region object
region <- Region(name = "nebraska", type = "us state",
                 div = c(country = "United States", state = "Nebraska"))

# Take a look at the data
head(data_progress$Corn)
```

### Model Creation

The package is built using the S4 class system, offering simplicity to new R users as well as ease of development to the project core team. Functions require a single object that holds all the necessary information concerning the model of interest. These objects are of class `ProgressModel` and can be concatenated into an object of class `ProgressModelList`.

```{r creation}
# Create a model
object1 <- new("ProgressBM",
               region = region,
               crop = "Corn",
               data = data_progress$Corn,
               formula = "CumPercentage ~ Time + agdd") # ProgressModel

# Create another model
object2 <- new("ProgressCLM",
               region = region,
               crop = "Soybeans",
               data = data_progress$Soybeans,
               formula = "Stage ~ Time + agdd + adayl") # ProgressModel

# Concatenate the models
object <- c(object1, object2) # ProgressModelList

# Tools
get_crops(object)
get_region(object)
get_index(object, crop = "Corn")
get_stages(object)
get_seasons(object)
```

### Fitting

Fitting the object is straightforward with the function `fit()`, which takes a
`ProgressModel` or `ProgressModelList` object and alters its `model` and `fitted` slots.

```{r fitting}
object <- fit(object)
plot(object, cumulative = TRUE, seasons = 2002)
```

### Prediction

The function `predict()` can take an object that has already been fitted and calculate the model predictions on a different dataset.

```{r prediction}
predict(object, data_progress)
```

### Evaluation

The evaluation of a model can be achieved with the `evaluate()` function, which performs Monte-Carlo (or leave-group-out) cross validation and alters the object's `metrics` slots.

```{r evaluation}
object <- evaluate(object, maxsam = 100, seed = 1)
object[[1]]@metrics
plot_rmspe(object[[1]])
```

### Summary

Function `summary()` can be used to get a brief presentation of the object.

```{r summary}
summary(object)
```

### Report

Instead of executing the above functions interactively, an html report including fitting, evaluation and summary of the model can be generated with the function `report()`. 

```{r report, eval = FALSE}
report(object, name = "example_report", path = getwd())
```
